Discovery of s-process stars in the LAMOST survey

### 2018-02-06 article/ms.tex
text updates; add mike summary

\author[B.~J. Norfolk et al.]{B.~J. Norfolk,$^{1}$\thanks{E-mail: bjee7@student.monash.edu (MU)}
A.~R. Casey,$^{1,2}$
M.~T. Miles,$^{1}$
A.~J. Kemp,$^{1}$ 
A.~I. Karakas,$^{1}$ \newauthor
J.~C. Lattanzio,$^{1}$
K.~C. Schlaufman,$^{3}$
and A.~Y.~Q. Ho$^{4}$
\\
$^{1}$School of Physics \& Astronomy, Monash University, Clayton 3800, Victoria, Australia\\
$^{2}$Faculty of Information Technology, Monash University, Clayton 3800, Victoria, Australia\\
$^{3}$Department of Physics and Astronomy, Johns Hopkins University, 3400 N Charles St., Baltimore, MD 21218, USA\\
$^{4}$Cahill Center for Astrophysics, California Institute of Technology, MC 249-17, 1200 E California Blvd, Pasadena, Ca, 91125, USA
}
\date{Accepted XXX. Received YYY; in original form ZZZ}

@@

\begin{abstract}
Stars with peculiar enhancements of carbon and heavy elements ($Z > 30$) are historically referred to as `Barium stars'. While this chemical abundance pattern can be explained by thermally pulsing asymptotic giant branch (AGB) stars, many so-called Barium stars have not evolved through the red giant phase and therefore cannot be AGB stars. These less-evolved stars are generally thought to have accreted mass from a more-evolved AGB companion. For this reason the frequency and properties of less-evolved Barium stars are uniquely informative on the binary fraction, AGB yields, mass transfer, and stellar evolution. Here we present the discovery of 967 s-process candidates from 454,180 giant stars observed by LAMOST. Our sample includes; 257 `Barium stars' that show enhancement in both barium and strontium, 49 stars showing only significant barium enhancement, and 661 exhibiting only strontium enhancement. This sample constitutes the largest number of s-process enhanced stars ever discovered, and represents the most comprehensive search for Barium stars in the Milky Way. We find up to 51 Barium stars exhibit some evidence of technetium from LAMOST spectra, and most (46/51) have $\log{g}>2$, which suggests they cannot be AGB stars and may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event. Most (178/257) Barium stars in our sample show strong carbon enhancement, consistent with the literature. However, despite previous claims indicating that Barium stars are preferentially enhanced in sodium due to the NeNa nucleosynthesis cycle occurring in massive AGB stars, only 5 ($<2$\,\%) of our Barium stars show any evidence of enhancement in sodium. A comparison with AGB yields suggests that the majority of our sample are consistent with a bottom-heavy IMF. When binary properties become available from end-of-mission Gaia astrometry, this sample of s-process stars will be critical in explaining mass transfer in binary systems and refining AGB yields across a range of masses and metallicities.
\end{abstract}

@@

The slow neutron capture process (s-process), occurring in the interior of AGB stars, synthesises roughly half of all elements heavier than iron \citep[e.g.,][]{busso1999,travaglio2001,herwig2005,romano2010,kobayashi2011,prantzos2012,bisterzo2014,karakas12016}. Late in the AGB phase, during the thermally pulsing-AGB (TP-AGB) phase, thermal instabilities occur in the He shell every $10^5$ years or so, depending on the H-exhausted core mass. These energy bursts drive a convective zone that sweeps the entire region lying between the core mass and He-shell; mixing the products of nucleosynthesis within these regions. The energy from the thermal pulses force the star to expand, pushing the H-shell out to cooler regions and allowing the convective envelope to move inwards to regions previously mixed by the thermal pulse driven convective zones. This expansion and resulting inward movement is described as the third dredge up (TDU), and is theorised to occur after each thermal pulse. During the TP-AGB phase, enrichment on the surface in $^{12}$C and heavy elements produced by the s-process is a result of the repeated downwash extensions of TDU \citep[e.g.,][]{busso2001}. The star contracts PDU and reignites the H-shell producing the majority of the surface luminosity for the next interpulse period. The interpulse, thermal pulse, and dredge up cycle may occur numerous times and is dependent on the initial mass, composition, and mass-loss rate of the star.

@@

Many Barium stars have been discovered in the disk and halo of the Milky Way \citep{gomez1997,mennessier1997}. 
%These studies show that the stellar populations of Barium stars can be separated into two groups when considering their absolute luminosity, kinematic, and spatial properties. 
The relationship between Barium stars in the halo \citep[e.g.,][]{junqueira2001,drake2008,pereira2009,allen2006} and metal-poor, yellow, symbiotic halo stars has been established by \citet{jorissen2005} and \citet{pereira2009}. Additionally, \citet{pereira2011} concludes that metal-rich Barium stars share similar kinematics to other metal-rich and super metal-rich stars already analysed, suggesting that they do not belong to the bulge population. Furthermore, it is necessary to establish known abundances of s-process elements in a greater sample of Barium stars in order to compare their birth rate to theoretical expectations \citep{han1995}, explore the binary fraction at different metallicities, and compare to AGB star yields at different masses and metallicities.

@@

\subsubsection{Candidate selection} \label{sec:cand}
The Barium stars analysed in this research were obtained by filtering for significant flux residuals, taken as, a disparity between the normalised LAMOST flux and the data driven model derived by \citet{ho2017}. Specifically, we identified Barium stars by searching for \ion{Ba}{II} and \ion{Sr}{II} enhancement at the 4554\,\AA\ and 4077\,\AA\ wavelengths, respectively. A negative residual, as shown in a candidate Barium star in Figure \ref{fig:figure1}, illustrates an enhancement in \ion{Ba}{II} and \ion{Sr}{II} at lines 4554\,\AA\, 4077\,\AA. These \ion{Ba}{II} and \ion{Sr}{II} resonance lines are very strong, allowing us to identify stars enhanced in neutron-capture elements given a well-fit model for the data. Stars identified to just show high levels of barium (and not necessarily strontium) required enhancement at both the 4554\,\AA\ and 4934\,\AA\ \ion{Ba}{II} resonance lines, and for stars just enhanced in strontium we looked for significant residuals at the 4554\,\AA\ and 4215\,\AA\ absorption lines.

@@

For the remainder of this paper we restrict our analysis to the 257 classical `Barium stars' stars that show enhancement in both barium and strontium. While the 49 or 661 stars with only barium or strontium enhancements (respectively) may also be bonafide barium stars, there may be other explanations for their chemical abundance pattern \citep[e.g.,][]{maiorca2011}, and so we restrict our inferences to a gold sample of Barium stars. Nevertheless, this sample still constitutes the largest collection of Barium stars ever discovered; the stellar sample given in \citet{decastro2016} constitutes the next largest Barium star candidate list.

\begin{figure*}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\textwidth]{posterchild.png}
    \caption{Pseudo-continuum-normalised LAMOST spectra for the s-process candidate \todo{CANDIDATENAME}. The data are shown in black and the best-fitting data-driven model is shown in red. We include zoom-in axes to show significant deviations in Sr and Ba at  4077\,\AA\ and 4554\,\AA\, respectively.}
    \label{fig:figure1}
\end{figure*}

\begin{table*}
\centering
\caption{Table is available online in its entirety. Here we show a portion to demonstrate its style and content.}
\label{table:table1}
\begin{adjustbox}{width=1\textwidth}
\begin{tabular}{@{}|l|l|c|c|c|c|c|c|c|c|c|c|c|c|c|c|@{}}
\toprule
2MASSID             & R.~A.         & Dec.        & $v_{r}$ & S/N & $\rm T_{\rm eff}$ & $\log{g}$ & [Fe/H] & [$\alpha$/Fe] & $\chi_r^2$ & [Ba/Fe] & [Sr/Fe] & \ion{Ba}{II} & \ion{Sr}{II} &  \ion{Ba}{II}\& \ion{Sr}{II} & Tc\\
& (J2000) & (J2000) & (km\,s$^{-1}$) & (pixel$^{-1}$) & (K)  \\ \midrule
J000019.26+501444.8 & 00:00:19.27 & +50:14:44.9 & -3.9  & 49      & 4973         & 3.27         & 0.21         & 0.08             & 0.66               & 0.25        & 0.83        & \ding{55} & \ding{51}  & \ding{55} & \ding{55}   \\
J000020.55+411348.1 & 00:00:20.56 & +41:13:48.2 & -28.2 & 32      & 4882         & 2.74         & -0.22        & 0.04             & 0.23               & -0.17       & 0.90        & \ding{55}& \ding{51}  & \ding{55} & \ding{55}    \\
J000134.95+490743.2 & 00:01:34.96 & +49:07:43.2 & -42.3 & 72      & 5044         & 3.11         & -0.54        & 0.11             & 0.79               & 1.02        & 0.45        & \ding{55} & \ding{55} & \ding{51}  & \ding{55}   \\
J000258.09+410730.0 & 00:02:58.10 & +41:07:30.1 & -34.5 & 41      & 4697         & 2.57         & -0.22        & 0.12             & 0.98               & -0.10       & 0.80        & \ding{55} & \ding{51}  & \ding{55}  & \ding{55}   \\
J000403.80+160257.1 & 00:04:03.80 & +16:02:57.2 & -35.4 & 42      & 5200         & 3.40         & -0.41        & 0.09             & 0.33               & 0.92        & 0.52        & \ding{55} & \ding{55} & \ding{51}  & \ding{55}   \\
J000439.16+183350.3 & 00:04:39.17 & +18:33:50.4 & -38.7 & 31      & 4601         & 2.50         & 0.44         & 0.03             & 0.34               & -0.11       & 0.88        & \ding{55} & \ding{51}  & \ding{55}  & \ding{55}   \\
J000444.87+400402.1 & 00:04:44.88 & +40:04:02.1 & -94.7 & 53      & 4172         & 1.46         & -0.08        & 0.09             & 0.72               & 0.03        & 0.91        & \ding{55} & \ding{51}  & \ding{55} & \ding{55}    \\
J000552.76+261849.3 & 00:05:52.76 & +26:18:49.4 & -22.5 & 73      & 4924         & 3.14         & -0.05        & 0.09             & 0.67               & 0.28        & 0.85        & \ding{55} & \ding{51}  & \ding{55} & \ding{55}    \\
J000737.70+394055.5 & 00:07:37.70 & +39:40:55.6 & -31.5 & 33      & 4700         & 2.80         & -0.04        & 0.07             & 0.28               & -0.13       & 0.81        & \ding{55} & \ding{51}  & \ding{55} & \ding{55}     
\end{tabular}
\end{adjustbox}
\end{table*}

@@

For technetium enhancement we searched for significant residual deviations at the 4049\,\AA, 4238\,\AA, 4262\,\AA, 4297\,\AA, and 5924\,\AA. These absorption lines are extremely weak, and would require a substantial amount of technetium before it would be visible in a high S/N LAMOST spectrum. We found 51 Barium stars exhibited some level of significant enhancement (based on the filters above) at a single technetium line, yet none showed enhancement at more than one technetium line. We note that the single enhancement near technetium for these 51 stars may be the consequence of data reduction/calibration artefacts, but we include details of which stars matched on technetium in Table \ref{table:table1} nonetheless.
Finally, for carbon enhancement we searched for significant deviations at the CH and G band near 4300\,\AA. We found 178/257 stars to show significant carbon enhancement (e.g., $[\textrm{C/Fe}] \gtrsim 0.5$).

\subsubsection{Abundance analysis from LAMOST spectra}
We estimated [Ba/Fe] and [Sr/Fe] abundance ratios for all s-process candidates by synthesising spectra that would account for the observed flux residuals. We assumed that absorption due to metals is captured by \emph{The Cannon} model, and deviations in flux at the 4554\,\AA\ \ion{Ba}{II} line and the 4077\,\AA\ \ion{Sr}{II} transition are solely due to enhancements in Ba and Sr, respectively\citep{marcs,sme,vald,ispec}. We adopted the stellar parameters ($T_{\rm eff}$, $\log{g}$, [Fe/H]) from \citep{ho2017}, and assume a microturbulence of $v_{mic} = 2\,{\rm km\,s}^{-1}$. Uncertainties in [Ba/Fe] and [Sr/Fe] from LAMOST are taken as the fitting error due to noise, added in quadrature with an adopted $0.2\,{\rm dex}$ systematic error floor.

@@

\subsubsection{Observations}
On the night of \todo{X} January 2018 we performed follow-up observations of \todo{X} Barium star candidates using the MIKE spectrograph on the Magellan Clay telescope at Las Campanas Observatory, Chile. Candidates for follow-up observations were chosen based on observability constraints and ranked by their apparent visual magnitude. We observed \todo{X} stars in good seeing using the 0.7 arcsecond slit and 2x2 spatial on-chip binning, which provides a spectral resolution of ($\mathcal{R} \approx \todo{22,000}$). Exposure times were set to achieve a S/N ratio of 30 per pixel at 4500\,\AA. We acquired calibration (biases, milky, quartz, and Th-Ar arc lamp) frames in the afternoon.

@@

\subsubsection{Abundance analysis}
We adopted the stellar parameters ($T_{\rm eff}$, $\log_{10}g$, [Fe/H]) provided from the data-driven analysis of \citep{ho2017}. Following the procedure outlined in \citep{casey2014}, we measured the strength of atomic absorption lines by fitting Gaussian profiles to the continuum-normalised spectra. Most elemental abundances were derived directly from these line measurements, except for elements that show significant hyperfine splitting \todo{(e.g., )} or blending \todo{(e.g., X)}. In these situations, we adopted a spectral synthesis approach. \todo{citations for line lists}

\todo{Some sentences for our fearless leader to add regarding abundance analysis and verification of stellar parameters from LAMOST}

@@

>>>>

\author[B.~J. Norfolk et al.]{B.~J. Norfolk,$^{1}$\thanks{E-mail: bjee7@student.monash.edu (MU)}
A.~R. Casey,$^{1,2}$
M.~T. Miles,$^{1}$
A.~J. Kemp,$^{1}$ 
A.~I. Karakas,$^{1}$\newauthor
A.~Y.~Q. Ho,$^{3}$
J.~C. Lattanzio,$^{1}$
K.~C. Schlaufman,$^{4}$
\\
$^{1}$School of Physics \& Astronomy, Monash University, Clayton 3800, Victoria, Australia\\
$^{2}$Faculty of Information Technology, Monash University, Clayton 3800, Victoria, Australia\\
$^{3}$Cahill Center for Astrophysics, California Institute of Technology, MC 249-17, 1200 E California Blvd, Pasadena, Ca, 91125, USA\\
$^{4}$Department of Physics and Astronomy, Johns Hopkins University, 3400 N Charles St., Baltimore, MD 21218, USA
}
\date{Accepted XXX. Received YYY; in original form ZZZ}

@@

\begin{abstract}
Stars with peculiar enhancements of carbon and heavy elements ($Z > 30$) are historically referred to as `Barium stars'. While this chemical abundance pattern can be explained by thermally pulsing asymptotic giant branch (AGB) stars, many so-called Barium stars have not evolved through the red giant phase and therefore cannot be AGB stars. These less-evolved stars are generally thought to have accreted mass from a more-evolved AGB companion. For this reason the frequency and properties of less-evolved Barium stars are uniquely informative on the binary fraction, AGB yields, mass transfer, and stellar evolution. Here we present the discovery of 967 s-process candidates from 454,180 giant stars observed by LAMOST. Our sample includes; 257 `Barium stars' that show enhancement in both barium and strontium, 49 stars showing only significant barium enhancement, and 661 exhibiting only strontium enhancement. This sample constitutes the largest number of s-process enhanced stars ever discovered. We find up to 51 Barium stars exhibit some evidence of technetium from LAMOST spectra, and most (46/51) have $\log{g}>2$, which suggests they cannot be AGB stars and may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event. Most (178/257) Barium stars in our sample show strong carbon enhancement, consistent with the literature. However, despite previous claims indicating that Barium stars are preferentially enhanced in sodium due to the NeNa nucleosynthesis cycle occurring in massive AGB stars, only 5 ($<2$\,\%) of our Barium stars show any evidence of sodium enhancement. A comparison with AGB yields suggests that the majority of our sample are consistent with a bottom-heavy initial mass function. When binary properties become available from end-of-mission Gaia astrometry, this sample of s-process stars will be critical in explaining mass transfer in binary systems and refining AGB yields across a range of masses and metallicities.
\end{abstract}

@@

The slow neutron capture process (s-process), occurring in the interior of AGB stars, synthesises roughly half of all elements heavier than iron \citep[e.g.,][]{busso1999,travaglio2001,herwig2005,romano2010,kobayashi2011,prantzos2012,bisterzo2014,karakas12016}. Late in the AGB phase, during the thermally pulsing-AGB (TP-AGB) phase, thermal instabilities occur in the He shell every $10^5$ years or so, depending on the H-exhausted core mass. These energy bursts drive a convective zone that sweeps the entire region lying between the core mass and He-shell; mixing the products of nucleosynthesis within these regions. The energy from the thermal pulses force the star to expand, pushing the H-shell out to cooler regions and allowing the convective envelope to move inwards to regions previously mixed by the thermal pulse driven convective zones. This expansion and resulting inward movement is described as the third dredge up (TDU), and is theorised to occur after each thermal pulse. During the TP-AGB phase, enrichment on the surface in $^{12}$C and heavy elements produced by the s-process is a result of the repeated downwash extensions of TDU \citep[e.g.,][]{busso2001}. The star contracts after dredge up and reignites the H-shell producing the majority of the surface luminosity for the next interpulse period. The interpulse, thermal pulse, and dredge up cycle may occur numerous times and is dependent on the initial mass, composition, and mass-loss rate of the star.

@@

Many Barium stars have been discovered in the disk and halo of the Milky Way \citep{gomez1997,mennessier1997}. 
%These studies show that the stellar populations of Barium stars can be separated into two groups when considering their absolute luminosity, kinematic, and spatial properties. 
The relationship between Barium stars in the halo \citep[e.g.,][]{junqueira2001,drake2008,pereira2009,allen2006} and metal-poor, yellow, symbiotic halo stars has been established by \citet{jorissen2005} and \citet{pereira2009}. \citet{pereira2011} also concludes that metal-rich Barium stars share similar kinematics to other metal-rich and super metal-rich stars already analysed, suggesting that they do not belong to the bulge population. It remains necessary to establish known abundances of s-process elements in a greater sample of Barium stars in order to compare their birth rate to theoretical expectations \citep{han1995}, explore the binary fraction at different metallicities, and compare to AGB star yields at different masses and metallicities.

@@

\subsubsection{Candidate selection} \label{sec:cand}
The Barium stars analysed in this research were obtained by filtering for significant flux residuals, taken as, a disparity between the normalised LAMOST flux and the data driven model derived by \citet{ho2017}. Specifically, we identified Barium stars by searching for \ion{Ba}{II} and \ion{Sr}{II} enhancement at the 4554\,\AA\ and 4077\,\AA\ wavelengths, respectively. A negative residual, as shown in a candidate Barium star in Figure \ref{fig:figure1}, illustrates an enhancement in \ion{Ba}{II} and \ion{Sr}{II} at lines 4554\,\AA\, and 4077\,\AA, respectively. These \ion{Ba}{II} and \ion{Sr}{II} resonance lines are very strong, allowing us to identify stars enhanced in neutron-capture elements given a well-fit model for the data. Stars identified to just show high levels of barium (and not necessarily strontium) required enhancement at both the 4554\,\AA\ and 4934\,\AA\ \ion{Ba}{II} resonance lines, and for stars just enhanced in strontium we looked for significant residuals at the 4554\,\AA\ and 4215\,\AA\ absorption lines.

@@

For the remainder of this paper we restrict our analysis to the 257 classical `Barium stars' stars that show enhancement in both barium and strontium. While the 49 or 661 stars with only barium or strontium enhancements (respectively) may also be bonafide barium stars, there may be other explanations for their chemical abundance pattern \citep[e.g.,][]{maiorca2011}, and so we restrict our inferences to a `gold sample' of Barium stars. Nevertheless, this sample still constitutes the largest collection of Barium stars ever discovered \citep[e.g.,][]{decastro2016}.

\begin{figure*}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\textwidth]{posterchild.png}
    \caption{Pseudo-continuum-normalised LAMOST spectra for the s-process candidate J064451.11+263239.2. The data are shown in black and the best-fitting data-driven model is shown in red. We include zoom-in axes to show significant deviations in Sr and Ba at  4077\,\AA\ and 4554\,\AA\, respectively.}
    \label{fig:figure1}
\end{figure*}

\begin{table*}
\centering
\caption{Table is available online in its entirety. Here we show a portion to demonstrate its style and content.}
\label{table:table1}
\begin{adjustbox}{width=1\textwidth}
\begin{tabular}{@{}|l|l|c|c|c|c|c|c|c|c|c|c|c|c|c|c|@{}}
\toprule
2MASSID             & R.~A.         & Dec.        & $v_{r}$ & S/N & $\rm T_{\rm eff}$ & $\log{g}$ & [Fe/H] & [$\alpha$/Fe] & $\chi_r^2$ & [Ba/Fe] & [Sr/Fe] & \ion{Ba}{II} & \ion{Sr}{II} &  \ion{Ba}{II} \& \ion{Sr}{II} & Tc\\
& (J2000) & (J2000) & (km\,s$^{-1}$) & (pixel$^{-1}$) & (K)  \\ \midrule
J000019.26+501444.8 & 00:00:19.27 & +50:14:44.9 & -3.9  & 49      & 4973         & 3.27         & 0.21         & 0.08             & 0.66               & 0.25        & 0.83        & \ding{55} & \ding{51}  & \ding{55} & \ding{55}   \\
J000020.55+411348.1 & 00:00:20.56 & +41:13:48.2 & -28.2 & 32      & 4882         & 2.74         & -0.22        & 0.04             & 0.23               & -0.17       & 0.90        & \ding{55}& \ding{51}  & \ding{55} & \ding{55}    \\
J000134.95+490743.2 & 00:01:34.96 & +49:07:43.2 & -42.3 & 72      & 5044         & 3.11         & -0.54        & 0.11             & 0.79               & 1.02        & 0.45        & \ding{55} & \ding{55} & \ding{51}  & \ding{55}   \\
J000258.09+410730.0 & 00:02:58.10 & +41:07:30.1 & -34.5 & 41      & 4697         & 2.57         & -0.22        & 0.12             & 0.98               & -0.10       & 0.80        & \ding{55} & \ding{51}  & \ding{55}  & \ding{55}   \\
J000403.80+160257.1 & 00:04:03.80 & +16:02:57.2 & -35.4 & 42      & 5200         & 3.40         & -0.41        & 0.09             & 0.33               & 0.92        & 0.52        & \ding{55} & \ding{55} & \ding{51}  & \ding{55}   \\
J000439.16+183350.3 & 00:04:39.17 & +18:33:50.4 & -38.7 & 31      & 4601         & 2.50         & 0.44         & 0.03             & 0.34               & -0.11       & 0.88        & \ding{55} & \ding{51}  & \ding{55}  & \ding{55}   \\
J000444.87+400402.1 & 00:04:44.88 & +40:04:02.1 & -94.7 & 53      & 4172         & 1.46         & -0.08        & 0.09             & 0.72               & 0.03        & 0.91        & \ding{55} & \ding{51}  & \ding{55} & \ding{55}    \\
J000552.76+261849.3 & 00:05:52.76 & +26:18:49.4 & -22.5 & 73      & 4924         & 3.14         & -0.05        & 0.09             & 0.67               & 0.28        & 0.85        & \ding{55} & \ding{51}  & \ding{55} & \ding{55}    \\
J000737.70+394055.5 & 00:07:37.70 & +39:40:55.6 & -31.5 & 33      & 4700         & 2.80         & -0.04        & 0.07             & 0.28               & -0.13       & 0.81        & \ding{55} & \ding{51}  & \ding{55} & \ding{55}     \\ \hline
\end{tabular}
\end{adjustbox}
\end{table*}

@@

For technetium enhancement we searched for significant residual deviations at 4049\,\AA, 4238\,\AA, 4262\,\AA, 4297\,\AA, and 5924\,\AA. These absorption lines are extremely weak, and would require a substantial amount of technetium before it would be visible in a high S/N LAMOST spectrum. We found 51 Barium stars exhibited some level of significant enhancement (based on the filters above) at a single technetium line, yet none showed enhancement at more than one technetium line. We note that the single enhancement near technetium for these 51 stars may be the consequence of data reduction/calibration artefacts, but we include details of which stars matched on technetium in Table \ref{table:table1} nonetheless.
Finally, for carbon enhancement we searched for significant deviations at the CH and G band near 4300\,\AA. We found 178/257 stars to show significant carbon enhancement (i.e., $[\textrm{C/Fe}] \gtrsim 0.5$).

\subsubsection{Abundances estimated from LAMOST spectra}
We estimated [Ba/Fe] and [Sr/Fe] abundance ratios for all s-process candidates by synthesising spectra that would account for the observed flux residuals. We assumed that absorption due to metals is captured by \emph{The Cannon} model, and deviations in flux at the 4554\,\AA\ \ion{Ba}{II} line and the 4077\,\AA\ \ion{Sr}{II} transition are solely due to enhancements in Ba and Sr, respectively \citep{marcs,sme,vald,ispec}. We adopted the stellar parameters ($T_{\rm eff}$, $\log{g}$, [Fe/H]) from \citep{ho2017}, and assume a microturbulence of $v_{mic} = 2\,{\rm km\,s}^{-1}$. Uncertainties in [Ba/Fe] and [Sr/Fe] from LAMOST are taken as the fitting error due to noise, added in quadrature with an adopted $0.2\,{\rm dex}$ systematic error floor.

@@

\subsubsection{Observations and data reduction}
On the night of 07 January 2018 we acquired a high-resolution spectrum of two Barium star candidates (J09162834+0259348 and J08351472-0548480) using the MIKE spectrograph on the Magellan Clay telescope at Las Campanas Observatory, Chile. Candidates for follow-up observations were chosen based on observability constraints and ranked by their apparent visual magnitude, with both candidates having $V \approx 12$. We observed both stars in good seeing using the 0.7 arcsecond slit and 2x2 spatial on-chip binning, providing a spectral resolution of ($\mathcal{R} \approx 28,000$). Exposure times of 100 seconds were sufficient to achieve a S/N ratio exceeding 30 per pixel at 4500\,\AA. We acquired calibration (biases, milky, quartz, and Th-Ar arc lamp) frames in the afternoon.

@@

\subsubsection{Abundance analysis}
We adopted the stellar parameters ($T_{\rm eff}$, $\log_{10}g$, [Fe/H]) provided from the data-driven analysis of \citep{ho2017}. Following the procedure outlined in \citep{casey2014}, we measured the strength of \ion{Ba}{II} (4554\,\AA, 4934\,\AA, and 6496\,\AA) and \ion{Sr}{II} (4077\,\AA\ and 4215\,\AA) absorption lines by spectral synthesis, using s-process isotopic ratios from \citet{sneden08}. The abundance ratios we estimate from high-resolution spectra are in excellent agreement with our estimates from LAMOST spectra, all agreeing within the joint $1.2\sigma$. Specifically, for J09162834+02593480 from high- and low-resolution spectra, respectively, we find $[{\rm Sr/Fe}] = 0.76 \pm 0.10$ and $0.85 \pm 0.21$, and $[{\rm Ba/Fe}] = 0.92 \pm 0.10$ and $0.77 \pm 0.21$. The biggest discrepancy we find between high- and low-resolution spectra is [Sr/Fe] for J09162834+0259348, where we find $[{\rm Sr/Fe}] = 0.62 \pm 0.07$ and $0.90 \pm 0.22$ from Magellan/MIKE and LAMOST, respectively. Finally, for J09162834+0259348 we find $[{\rm Ba/Fe}] = 0.94 \pm 0.12$ from high-resolution spectra and $[{\rm Ba/Fe}] = 0.80 \pm 0.26$ from low-resolution spectra. Uncertainties on abundances derived from high-resolution spectra are taken as the standard deviation of multiple line measurements.

@@

\bibitem[Sneden et al.(2008)]{sneden08} Sneden, C., Cowan, J.~J., \& Gallino, R.\ 2008, \araa, 46, 241 
